The role of priors, competence and relevance for the interpretation of disjunction \thanks{We thank \ldots}

### 2022-02-08 writing/paper/paper_draft.tex
pass over intro section and exploratory analyses

General intuition, introduction \citep[e.g.,][]{horn1972semantic}.
 \pt{ported over from old paper below}
Introductions to logic usually distinguish between two readings of “or”: an inclusive
and an exclusive reading (e.g., McCawley, 1981; Copi \& Cohen, 2005). The inclusive
reading corresponds to the meaning of logical disjunction. According to this reading,
“A or B” is true if at least one and possibly both of A and B are true. The exclusive
reading is more strict in that it excludes the possibility that both A and B are true. So
on its exclusive reading, “A or B” is true if exactly one of A and B is true. The presence of these two readings might suggest that “or” is associated with two
different lexical entries (e.g., Basson \& O’Connor, 1960; Baum, 1996; Rescher, 1964).
There are, however, good reasons to reject such a lexicalist approach. Perhaps the most
compelling reason is that, in some contexts, “or” can only receive one interpretation.
To illustrate, consider the following sentence, in which “or” occurs in the scope of
negation: (2) Joe does not support Donald or Hillary.
This sentence has only one interpretation, namely that Joe supports neither Donald nor
Hillary (cf. Crain, 2008). This interpretation corresponds to the inclusive reading of
“or”. It does not have an interpretation corresponding to the exclusive reading; in other
words, it does not have a reading according to which Joe either supports both Donald
and Hillary, or neither of them. Since “or” is systematically monosemous in certain
contexts—negation being one of them—it follows that the two readings of “or” cannot
simply be due to a lexical ambiguity.
An attractive alternative to the lexicalist approach stems from Grice’s (1975) theory
of conversational implicature. According to Grice, natural conversation is governed by
the assumption that speakers are cooperative; that is, they attempt to further the purpose
of the discourse by means of their utterances. Speakers are cooperative by adhering
to four maxims that enjoin their utterances to be truthful, informative, relevant,
and clear. Sometimes hearers have to make ancillary assumptions in order to align a
speaker’s utterance with the assumption of cooperativity. Such ancillary assumptions
are called conversational implicatures. Horn (1972) was the first to argue that the exclusive reading of “or” can be explained
as a conversational implicature, too, based on the assumption that the primary
meaning of “or” is inclusive. To illustrate, consider (1) again. Assuming that the primary
meaning of “or” is inclusive, the speaker of (1) could have been more informative,
and hence cooperative, by uttering the “and”-alternative “Joe supports Donald
and Hillary.” Why didn’t she? Presumably because she does not believe that the “and”-
alternative is true. This is a weak inference that is compatible with a situation in which
the speaker is unsure about whether or not Joe supports both Donald and Hillary. This
weak inference can be strengthened if there is reason to believe that the speaker knows
whether or not Joe supports both Donald and Hillary. This assumption is often called
the competence assumption (e.g., Geurts, 2010; Russell, 2006; Schulz \& van Rooij,
2006; Zimmermann, 2000). If the competence assumption is sufficiently plausible, it
follows that, according to the speaker, Joe does not support both Donald and Hillary.
This specific kind of conversational implicature is often called a scalar implicature
because it is assumed that “or” forms a lexical scale with “and”, and that alternatives
are generated by substituting the scalemates “or” and “and”. Other lexical scales are
hsome, alli, hwarm, hoti, and hintelligent, brillianti.

The implicature account straightforwardly explains the absence of exclusive readings
under negation. Consider (2) again. Here, unlike in the case of (1), the “and”-
alternative is less informative than the utterance itself. After all, (2) is only compatible
with a situation in which Joe supports neither Donald nor Hillary, whereas the
“and”-alternative is also consistent with situations in which Joe supports exactly one
of Donald and Hillary. So the speaker was already maximally informative and hence
no implicature is derived.
Although the implicature account has since become the standard in the literature
(e.g., Chevallier, Noveck, Nazir, Bott, Lanzetti, \& Sperber, 2008; Chierchia, Fox, \&
Spector, 2012; Geurts, 2010; Sauerland, 2004), it is not without its problems, as we
will see in the next section. Therefore, we set out to experimentally test the adequacy
of the implicature account. To that end, we investigated the effect of three factors on the
robustness of exclusive readings: (i) the relevance of the “and”-alternative to the hearer,
(ii) the competence of the speaker about the truth of the “and”-alternative, and (iii) the
prior probability that the “and”-alternative is true. These factors are usually taken to
influence the robustness of scalar implicatures. Hence, if the implicature account is
correct, we expect these factors to influence the robustness of the exclusive reading of
“or”, too, For comparison, we also investigated how relevance, competence, and prior probability
influence the robustness of a bona fide scalar implicature, namely the inference
from “some” to “not all”. To illustrate, consider:
(4) Some of my friends support Donald.
An utterance of this sentence may convey that not all of the speaker’s friends support
Donald. The derivation of this upper-bounded construal runs analogous to that of the
exclusive reading of “or”: the speaker could have been more informative by saying
“All of my friends support Donald”. Why didn’t she? Presumably because she does. not believe that this alternative is true. If, moreover, the speaker knows whether or
not all of her friends support Donald—i.e., if the speaker is competent in the relevant
sense—it follows that she believes that not all of her friends support Donald.
As we will see, it turns out that there are marked differences in how relevance,
competence, and prior probability influence the robustness of the exclusive reading of
“or” compared to how they influence the robustness of the inference from “some” to
“not all”. These findings will encourage us to reconsider the implicature account of the
exclusive reading of “or”. In the next section, we explain our three factors of interest in more detail. Afterwards, we outline the details of our experiments and discuss the results.

@@

SI accounts and treatments of ``some'' and ``or''.

\textbf{Related experimental/modelling work: } 
Some: \citep{degen2015investigating}, 
Or: \citep{Li2021}

@@

\subsection{Predictions}
Prior research has shown that the robustness of implicatures from ``some'' to ``some, but not all''  predicted by the standard scalar implicature (SI) account is influenced by three factors. First, high contextual relevance of the stronger alternative ``all'' to the listener is predicted to render more robust scalar implicatures. Second, high speaker competence about the truth of the stronger alternative is predicted to lead to more robust scalar implicature generation. Lastly, high prior probability of the stronger ``all'' being true is assumed to \textit{decrease} the scalar implicature rate.
If the currently standard scalar implicature account also holds for the interpretation of disjunctions, analogous predictions for the robustness of the implicature from ``A or B'' to ``A or B, but not both'' can be derived. In case of disjunction, the relevant stronger alternative is ``and''.

@@

More specifically, we conducted a simulation-based Bayesian power analysis which aimed at determining how many participants are required in order to detect a theoretically motivated conjunctive effect of the predictors prior, relevance and competence with a confidence of at least 0.8 \citep[e.g.,][]{degen2015investigating}. The simulations were based on an assumed effect size $\beta = 0.15$ for all predictors, and a Region Of Practical Equivalence (ROPE) $\delta = 0.05$ for judging evidence for the directionality of a coefficient given the data \citep{kruschke2014doing}. The simulations were further based on the maximal desired model justified theoretically and by the design.\footnote{The maximal model in R syntax is: \texttt{rating = trigger * prior * competence * relevance}. The random effects were omitted for computational tractability reasons and due to the lack of well-founded estimates of group-level effect sizes.}

For this analysis, hypothetical experimental data representing the predictor effect rating was simulated by drawing four samples from a standard Normal distribution $\mathcal{N}(0,1)$ per simulated subject. Next, the target inference strength rating was modelled as a sample from a normal distribution with the mean computed as the sum of the simulated predictor values weighted by the assumed effect size (0.15). Then, the desired maximal Bayesian regression model was computed on the simulated data. The described steps were performed for a number of subjects ranging from 100 up to 340, increased iteratively in steps of 20. For each number of subjects, the model was re-computed on the simulated samples for $k=100$ iterations. For each iteration $i_k$, the conjunctive hypothesis of interest was tested. 
The power for the given number of participants was calculated as the proportion of iterations for which the conjunctive hypothesis was credible (i.e., if the posterior probability ($P(\beta_X > \delta \mid D)$) was at least 0.95, for $\delta = 0.05$ was the parameter that defined our ROPE for the conjunction of all three predictor coefficients).

@@

Participants’ factor ratings by-story agreed well with the designed classification of the stories (Fig. \ref{main-raw-ratings}, red vs. blue color on x-axis).

@@

Given this model and the data, we found very similar results for both triggers: We observe a negative effect of prior and a positive effect of competence, in line with predictions of the scalar implicature hypothesis (Fig.\ref{posteriors-cat}). However, we again observe no effects of relevance. If anything, the relevance effect tends in the direction opposite to predictions of the SI account for the trigger ``or''.

@@

These results match the second exploratory analysis, whereby the ratings were used as predictors in the linear model, but the ratings were averaged for each vignette across participants. In this second  exploratory model, we again find similar effects for ``some'' and ``or'': a positive effect of competence, negative for prior, and an indefinite relevance effect (Fig.\ref{posteriors-mean}). By averaging over single participant ratings, this model indicates that the absent competence effect in the main model might be due to by-participant variation.

In order to further investigate the relevance effects and potential collinarity concerns, we computed exploratory pairwise correlations of all the predictors. Interestingly, we find a significant correlation between the prior and the relevance effects for the trigger ``or'' ($R^2 = -0.106$). We also found a significant correlation between competence and relevance ($R^2 = 0.127$) for ``or''. No correlations were found for ``some''. These intriguing results might indicate that these effects are closely related for disjunction. Intuitively, a negative correlation between prior and relevance of the stronger alternative ``and'' makes sense: the more likely the conjunction is a priori, the more likely it is that the listener might know about it already, yielding the implicature irrelevant to the listener. Similarly, competence might be connected to relevance indirectly via the prior: the more likely the stronger alternative is a priori, the more likely it is that a speaker knows about it, while the irrelevance still persists for the listener. However, this entangled results need further research.

Finally, we conduct an exploratory analysis when setting the ROPE to 0. That is, we investigate whether the posterior estimates for the regression coefficients of interest are positive ($>0$) or negative ($<0$) and interpret the data as providing evidence in favor of a particular direction if at least 95\% of posterior samples for the respective coefficent are positive or negative. As in the main analysis, we find credible positive effects of competence for both ``some'' ($P = 1$) and ``or'' ($P = 1$), and a credible negative effect of prior for ``some'' ($P = 1$), but not for ``or'' ($P=0.91$). However, in contrast to the main analysis, we do find a credible positive effect of relevance for ``or'' ($P=0.978$), but not for ``some'' ($P=0.829$). \pt{We should include justification for using a ROPE in the first place here}

\subsubsection{Model comparisons}
Because the correlations hint at possible collinearity effects between relevance and prior for the trigger ``or'', we conduct exploratory model comparisons. That is, in order to check whether certain factors among relevance, competence and prior have a stronger influence on the inference stength ratings, we compare regression models of different complexity. We take a Bayesian approach to model comparison here in terms of their Bayes factors \citep{rouder2012default}. 
We compare all regression models that can be built with the three explanatory factors as main factors against a baseline intercept-only model.\footnote{If the model contains more than one main effect, all interactions between main effects are always included in the model, as well. All justified and computationally tractable random effects are added to each model, respectively.}
Following literature, we interpret the evidence in favor of a particular model as strong if the odds (i.e., the Bayes Factor) are between are above 10, as mild, if they are between 3 and 10, and as absent if the odds are between 3 and 1/3 \citep[e.g.,][]{lodewyckx2011tutorial}.

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.8\linewidth]{images/BF_vs_SD_allModels_vs_int.pdf}
	\end{center}
	\vspace{-0.3cm}
	\caption{Bayes factor comparison of different main factor combinations.}
	\label{bf-grid-search}
\end{figure}

To investigate the stability of the Bayes factors of a certain model over the baseline, we conduct a grid search over the standard deviation parameter of the prior student-t distribution over the main effect regression coefficients. More precisely, given that, based on prior experimental work, the expected effect size for the main factors was around $\beta=0.15$, the standard deviation parameters considered in the grid search included {0.05, 0.1, 0.15}. Figure \ref{bf-grid-search} shows the Bayes factors against the intercept-only model of all the regression models plotted against the different standard deviation parameters of the priors. It indicates that, in general, the Bayes factor does not change strongly dependent on the tightness of the prior distribution. It further suggests that the intercept-only model is a better fit to the data than all of the explored regression models, but more so for models containing both relevance and prior as explanatory factors. This corroborates the finding based on the correlation, indicating that relevance and prior might be co-dependent and explain each other away. We also observe that models containing the effect of relevance are slightly less likely given the data than models containing the effect of prior, but the difference is negligible. However, these results might also be due to the fact that additional model complexity of the regression models overpowers potential improvement in model fit.

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.8\linewidth]{images/BF_vs_SD_rel-comp_pri-comp.pdf}
	\end{center}
	\vspace{-0.3cm}
	\caption{Bayes factor of the relevance*competence model over the prior*competence model.}
	\label{bf-rel-pri}
\end{figure}

Therefore, to zoom in on the comparison between the effects of relevance and prior on inference strength ratings we conduct further exploratory model comparisons. Specifically, we compare two-factor models, comparing relevance over prior, each combined with competence, respectively. As can be seen in Figure \ref{bf-rel-pri}, the Bayes factor varies more strongly depending on the standard deviation parameter of the prior distribution over the main regression coefficients. For $SD=0.05$, we find $BF=0.27$, indicating that ``prior'' model is around three times more likely than the ``relevance'' model, which can we consider mild evidence in favor of prior being the better predictor for the inference strength of exclusive disjunctions. 
Yet further investigation of the interaction between relavance and competence effects with respect to their influence on exclusive disjunctions is needed.

@@

Furthermore, our results hint at intriguing dependencies between relevance and prior effects for the interpretation of exclusive disjunctions. Taken together, the results might speak against the identity hypothesis, indicating that there might be subtle differences in the conceptualization of the stronger alternative for ``some'' and ``or''.

>>>>

\pt{Framing suggestion: start out with a general introduction on scalar implicature as applicable to both some and or,  give some details on why xor is also interesting. Ported over from abstract. Review prior work focusing on separate factors influencing SIs. Motivate our study.}

If someone says “Anna ate some cookies”, the hearer might infer the upper-bounded reading that Anna ate some, but not all cookies. Modern theories usually treat this inference as one of the prime examples of \textit{scalar implicature} (SI) \citep{horn1972semantic}. More specifically, the SI relies on a lexical scale consisting of words ordered in terms of informativeness (or, strength), like $\langle$some, all$\rangle$. When interlocutors encounter the weaker expression ``some'', the stronger ``all'' functions as a salient alternative \citep{matsumoto1995conversational}.

Theories of pragmatics suggest that interlocutors reason about these scales, guided by conversational pronciples introduced by \citet{grice1975logic}.
According to \citet{grice1975logic}, natural conversation is governed by
the assumption that speakers are cooperative; that is, they attempt to further the purpose
of the discourse by means of their utterances. Speakers are cooperative by adhering
to four maxims that enjoin their utterances to be truthful, informative, relevant,
and clear. Sometimes hearers have to make ancillary assumptions in order to align a
speaker’s utterance with the assumption of cooperativity. Such ancillary assumptions
are called conversational implicatures.
%Recent theories of pragmatics suggest that cooperative interlocutors reason about each other's utterances, guided by certain \textit{conversational maximes} \citep{grice1975logic}. 
That is, in case of ``some'', assuming a rational speaker who wishes to be maximally cooperative, the listener of the utterance would infer that if the stronger alternative (i.e., ``all'') was true, the speaker would have used the stronger utterance; but since she did not, she must have lacked the evidence for using ``all'' \citep{grice1975logic, goodman2016pragmatic}.

Similarly to the first example, given the utterance “Donald ate a donut or a pretzel.”, the listener might infer that Donald ate either the donut or the pretzel, but not both (i.e., an \textit{exclusive} interpretation).
%This inference can also be explained as a variety of scalar implicature, relying on the scale $\langle$or, and$\rangle$. If a speaker uses an informationally weaker term (e.g., “some”), they may imply that the corresponding stronger alternative (e.g., “and”) is false [3,5]. 
\pt{ported over from old paper below}

Introductions to logic usually distinguish between two readings of “or”: an inclusive
and an exclusive reading (e.g., McCawley, 1981; Copi \& Cohen, 2005). The inclusive
reading corresponds to the meaning of logical disjunction. According to this reading,
“A or B” is true if at least one and possibly both of A and B are true. The exclusive
reading is more strict in that it excludes the possibility that both A and B are true. So
on its exclusive reading, “A or B” is true if exactly one of A and B is true.

The standard account of exclusive readings of disjunction in the literature also stems from Grice’s (1975) theory of conversational implicature (e.g., Chevallier, Noveck, Nazir, Bott, Lanzetti, \& Sperber, 2008; Chierchia, Fox, \& Spector, 2012; Geurts, 2010; Sauerland, 2004). 
\citet{horn1972semantic} was the first to argue that the exclusive reading of “or” can be explained as a conversational implicature, too, based on the assumption that the primary meaning of “or” is inclusive. To illustrate, consider (1) again. Assuming that the primary
meaning of “or” is inclusive, the speaker of (1) could have been more informative,
and hence cooperative, by uttering the “and”-alternative “Joe supports Donald
and Hillary.” Why didn’t she? Presumably because she does not believe that the “and”-
alternative is true. This is a weak inference that is compatible with a situation in which
the speaker is unsure about whether or not Joe supports both Donald and Hillary. This
weak inference can be strengthened if there is reason to believe that the speaker knows
whether or not Joe supports both Donald and Hillary. This assumption is often called
the competence assumption (e.g., Geurts, 2010; Russell, 2006; Schulz \& van Rooij,
2006; Zimmermann, 2000). If the competence assumption is sufficiently plausible, it
follows that, according to the speaker, Joe does not support both Donald and Hillary.
For this conversational implicature it is assumed that “or” forms a lexical scale with “and” %, and that alternatives are generated by substituting the scalemates “or” and “and”. Other lexical scales are <some, all>, <warm, hot>, and <intelligent, brilliant>.

Alternative theories propose that the presence of these two readings might suggest that “or” is associated with two
different lexical entries (e.g., Basson \& O’Connor, 1960; Baum, 1996; Rescher, 1964).
There are, however, good reasons to reject such a lexicalist approach. Perhaps the most
compelling reason is that, in some contexts, “or” can only receive one interpretation.
To illustrate, consider the following sentence, in which “or” occurs in the scope of
negation: (2) Joe does not support Donald or Hillary.
This sentence has only one interpretation, namely that Joe supports neither Donald nor
Hillary (cf. Crain, 2008). This interpretation corresponds to the inclusive reading of
“or”. It does not have an interpretation corresponding to the exclusive reading; in other
words, it does not have a reading according to which Joe either supports both Donald
and Hillary, or neither of them. Since “or” is systematically monosemous in certain
contexts—negation being one of them—it follows that the two readings of “or” cannot
simply be due to a lexical ambiguity.

The implicature account straightforwardly explains the absence of exclusive readings
under negation. Consider (2) again. Here, unlike in the case of (1), the “and”-
alternative is less informative than the utterance itself. After all, (2) is only compatible
with a situation in which Joe supports neither Donald nor Hillary, whereas the
“and”-alternative is also consistent with situations in which Joe supports exactly one
of Donald and Hillary. So the speaker was already maximally informative and hence
no implicature is derived.
Although the implicature account has since become the standard in the literature
(e.g., Chevallier, Noveck, Nazir, Bott, Lanzetti, \& Sperber, 2008; Chierchia, Fox, \&
Spector, 2012; Geurts, 2010; Sauerland, 2004), it is not without its problems, as we
will see in the next section. 
\pt{end of section from old paper}

Crucially, prior research suggests that the robustness of SIs is influenced by different contextual factors.

@@

\textbf{Related experimental/modelling work: } 
Some: \citep{degen2015investigating, goodman2016pragmatic}, 
Or: \citep{Li2021}

@@

\subsection{Predictions}
Prior research has shown that the robustness of implicatures from ``some'' to ``some, but not all''  predicted by the standard scalar implicature (SI) account is influenced by three factors. First, high contextual relevance of the stronger alternative ``all'' to the listener is predicted to render more robust scalar implicatures. Second, high speaker competence about the truth of the stronger alternative is predicted to lead to more robust scalar implicature generation. Lastly, high prior probability of the stronger ``all'' being true is assumed to \textit{decrease} the scalar implicature rate. \pt{If the framing is okay, add some motivation and predictions regarding investigating the conjunction of these factors.}
If the currently standard scalar implicature account also holds for the interpretation of disjunctions, analogous predictions for the robustness of the implicature from ``A or B'' to ``A or B, but not both'' can be derived. In case of disjunction, the relevant stronger alternative is ``and''.

@@

More specifically, we conducted a simulation-based Bayesian power analysis which aimed at determining how many participants are required in order to detect a theoretically motivated conjunctive effect of the predictors prior, relevance and competence with a confidence of at least 0.8. The simulations were based on an assumed effect size $\beta = 0.15$ for all predictors \citep[e.g.,][]{degen2015investigating}, and a Region Of Practical Equivalence (ROPE) $\delta = 0.05$ for judging evidence for the directionality of a coefficient given the data \citep{kruschke2014doing}. That is, we determined how many participants would be necessary such that the regression coefficients |$\beta_X$| for the three predictors would be larger than $\delta$.
The simulations were further based on the maximal desired model justified theoretically and by the design.\footnote{The maximal model in R syntax is: \texttt{rating = trigger * prior * competence * relevance}. The random effects were omitted for computational tractability reasons and due to the lack of well-founded estimates of group-level effect sizes.}

For this analysis, hypothetical experimental data representing the predictor effect rating was simulated by drawing four samples from a standard Normal distribution $\mathcal{N}(0,1)$ per simulated subject per trigger. Next, the target inference strength rating was modelled as a sample from a normal distribution with the mean computed as the sum of the simulated predictor values weighted by the assumed effect size (0.15). Then, the desired maximal Bayesian regression model was computed on the simulated data. The described steps were performed for a number of subjects ranging from 100 up to 340, increased iteratively in steps of 20. For each number of subjects, the model was re-computed on the simulated samples for $k=100$ iterations. For each iteration $i_k$, the conjunctive hypothesis of interest was tested. 
The power for the given number of participants was calculated as the proportion of iterations for which the conjunctive hypothesis was credible (i.e., if the posterior probability $P(\beta_X > \delta \mid D)$ was at least 0.95, for $\delta = 0.05$ was the parameter that defined our ROPE for the conjunction of all three predictor coefficients). The target proportion was 0.8.

@@

Participants’ factor ratings by-story agreed well with the designed classification of the stories (Fig. \ref{main-raw-ratings}, red vs. blue color on x-axis). That is, the ratings for the relevance, comptence and prior statements were not distributed uniformly across the stories, but align with the prior categorization of the story for the respective factor (Fig. \ref{main-raw-ratings}, columns). This provides validation for our experimental manipulation of the explanatory factors.

@@

Given this model and the data, we found very similar results for both triggers: We observe a negative effect of prior and a positive effect of competence, in line with predictions of the scalar implicature hypothesis (Fig.~\ref{posteriors-cat}). However, we again observe no effects of relevance. If anything, the relevance effect tends in the direction opposite to predictions of the SI account for the trigger ``or''.

@@

These results match the second exploratory analysis, whereby the ratings were used as predictors in the linear model, but the ratings were averaged for each vignette across participants. In this second  exploratory model, we again find similar effects for ``some'' and ``or'': a positive effect of competence, negative for prior, and an indefinite relevance effect (Fig.~\ref{posteriors-mean}). By averaging over single participant ratings, this model indicates that the absent competence effect for the disjunction in the main model might be due to by-participant variation.

In order to further investigate the relevance effects and potential collinarity concerns, we computed exploratory pairwise correlations of all the predictors. Interestingly, we find a significant correlation between the prior and the relevance effects for the trigger ``or'' ($R^2 = -0.106$). We also found a significant correlation between competence and relevance ($R^2 = 0.127$) for ``or''. \pt{We should talk about the latter correlation in more detail at some point.} No correlations were found for ``some''. These intriguing results might indicate that these effects are closely related for disjunction. Intuitively, a negative correlation between prior and relevance of the stronger alternative ``and'' makes sense: the more likely the conjunction is a priori, the more likely it is that the listener might know about it already, yielding the implicature irrelevant to the listener. Similarly, competence might be connected to relevance indirectly via the prior: the more likely the stronger alternative is a priori, the more likely it is that a speaker knows about it, while the irrelevance still persists for the listener. However, these speculations call for further research.

Finally, we conduct an exploratory analysis when setting the ROPE to 0. That is, we investigate whether the posterior estimates for the regression coefficients of interest are positive ($>0$) or negative ($<0$) and interpret the data as providing evidence in favor of a particular direction if at least 95\% of posterior samples for the respective coefficent are positive or negative. As in the main analysis, we find credible positive effects of competence for both ``some'' ($P = 1$) and ``or'' ($P = 1$), and a credible negative effect of prior for ``some'' ($P = 1$), but not for ``or'' ($P=0.91$). However, in contrast to the main analysis, we do find a credible positive effect of relevance for ``or'' ($P=0.978$), but not for ``some'' ($P=0.829$). \pt{We should include justification for using a ROPE in the first place here. Some more discussion needs to be added too.}

\subsubsection{Model comparisons}
Because the correlations hint at possible collinearity effects between relevance and prior for the trigger ``or'', we conduct exploratory model comparisons. That is, in order to check whether certain factors among relevance, competence and prior have a stronger influence on the inference stength ratings than other, we compare regression models of different complexity. We take a Bayesian approach to model comparison here in terms of their Bayes factors \citep{rouder2012default}. 
We compare all regression models that can be built with the three explanatory factors as main factors against a baseline intercept-only model.\footnote{If the model contains more than one main effect, all interactions between main effects are always included in the model, as well. All justified and computationally tractable random effects are added to each model, respectively.}
Following literature, we interpret the evidence in favor of a particular model as strong if the odds (i.e., the Bayes Factor) are above 10 or below 1/10; as mild, if they are between 3 and 10 or 1/3 and 1/10; and as absent if the odds are between 3 and 1/3 \citep[e.g.,][]{lodewyckx2011tutorial}.

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=\linewidth]{images/BF_vs_SD_allModels_vs_int.pdf}
	\end{center}
	\vspace{-0.3cm}
	\caption{Bayes factor comparison of different main factor combinations (colors) for different standard deviation parameter values of the prior $t-$distribution over the main regression coefficients (x-axis). The log Bayes Factor (y-axis) is computed in favor the more complex model over an intercept-only model. \pt{Model names will be made human-readable, the title will be removed.}}
	\label{bf-grid-search}
\end{figure}

To investigate the stability of the Bayes factors of a certain model over the baseline, we conduct a grid search over the standard deviation parameter of the prior student-$t$ distribution over the main effect regression coefficients. More precisely, given that, based on prior experimental work, the expected effect size for the main factors was around $\beta=0.15$, the standard deviation parameters considered in the grid search included {0.05, 0.1, 0.15}. Figure \ref{bf-grid-search} shows the Bayes factors against the intercept-only model of all the regression models plotted against the different standard deviation parameters of the priors. It indicates that, in general, the Bayes factor does not change strongly dependent on the tightness of the prior distribution. It further suggests that the intercept-only model is a better fit to the data than all of the explored regression models, but more so for models containing both relevance and prior as explanatory factors. This corroborates the finding based on the correlation, indicating that relevance and prior might be co-dependent and explain each other away. We also observe that models containing the effect of relevance are slightly less likely given the data than models containing the effect of prior, but the difference is negligible. However, these results might also be due to the fact that additional model complexity of the regression models overpowers potential improvement in model fit.

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=\linewidth]{images/BF_vs_SD_rel-comp_pri-comp.pdf}
	\end{center}
	\vspace{-0.3cm}
	\caption{Bayes factor of the \texttt{relevance*competence} model over the \texttt{prior*competence model} (y-axis), plotted against different standard deviation parameter values of the prior $t-$distribution over the main regression coefficients (x-axis). \pt{The title will be removed.}}
	\label{bf-rel-pri}
\end{figure}

Therefore, to zoom in on the comparison between the effects of relevance and prior on inference strength ratings we conduct further exploratory model comparisons. Specifically, we compare two-factor models, comparing relevance over prior, each combined with competence, respectively. As can be seen in Figure \ref{bf-rel-pri}, the Bayes factor varies more strongly depending on the standard deviation parameter of the prior distribution over the main regression coefficients. For $SD=0.05$, we find $BF=0.27$, indicating that the model containing  the predictors \texttt{prior*competence } is around three times more likely than the \texttt{relevance*competence} model, which can we consider mild evidence in favor of prior being the better predictor for the inference strength of exclusive disjunctions. 
Yet further investigation of the interaction between relavance and competence effects with respect to their influence on exclusive disjunctions is needed.

@@

Furthermore, our results hint at intriguing dependencies between relevance and prior effects for the interpretation of exclusive disjunctions. Taken together, the results might speak against the identity hypothesis, indicating that there might be subtle differences in the conceptualization of the stronger alternative for ``some'' and ``or''. \pt{Focus on the aspect of interactions between the predictors more strongly.}
